### 2019-06-27 report/chapter03.Rnw
Results update

<<'preamble03',include=FALSE, echo=FALSE>>=
library(knitr)
opts_chunk$set(fig.path='figure/ch03_fig',
               echo=TRUE, message=FALSE,
               fig.width=8, fig.height=3,
               self.contained = FALSE,
               out.width='\\textwidth-3cm',
               message=FALSE, fig.align='center',
               background="gray98", tidy=FALSE, #tidy.opts=list(width.cutoff=60),
               cache=TRUE
)
options(width=74)
@

@@

@@

#Agreement proportions of publication bias tests:

#Binary:
meta.bin <- meta.bin %>%ungroup() %>%  mutate(tes.d.schwarzer = ifelse(tes.d.test == schwarzer.test, "agree", "disagree"),
																							tes.d.peter = ifelse(tes.d.test == peter.test, "agree", "disagree"),
																							tes.d.rucker = ifelse(tes.d.test == rucker.test, "agree", "disagree"),
																							tes.d.harbord = ifelse(tes.d.test == harbord.test, "agree", "disagree"),
																							schwarzer.peter = ifelse(schwarzer.test == peter.test, "agree", "disagree"),
																							schwarzer.rucker = ifelse(schwarzer.test == rucker.test, "agree", "disagree"),
																							schwarzer.harbord = ifelse(schwarzer.test == harbord.test, "agree", "disagree"),
																							rucker.peter = ifelse(rucker.test == peter.test, "agree", "disagree"),
																							rucker.harbord = ifelse(rucker.test == harbord.test, "agree", "disagree"),
																							harbord.peter = ifelse(harbord.test == peter.test, "agree", "disagree"))
agreement.bin <- meta.bin %>% ungroup() %>% summarise(tes.d.schwarzer = sum(tes.d.schwarzer == "agree")/n(),
																											tes.d.peter = sum(tes.d.peter == "agree")/n(),
																											tes.d.rucker = sum(tes.d.rucker == "agree")/n(),
																											tes.d.harbord = sum(tes.d.harbord == "agree")/n(),
																											schwarzer.peter = sum(schwarzer.peter == "agree")/n(),
																											schwarzer.rucker = sum(schwarzer.rucker == "agree")/n(),
																											schwarzer.harbord = sum(schwarzer.harbord == "agree")/n(),
																											rucker.peter = sum(rucker.peter == "agree")/n(),
																											harbord.peter = sum(harbord.peter == "agree")/n())
correlation.bin <- meta.bin %>%ungroup() %>%  summarise(tes.d.schwarzer = cor(pval.d.tes, pval.schwarzer),
																												tes.d.peter = cor(pval.d.tes, pval.peter),
																												tes.d.rucker = cor(pval.d.tes, pval.rucker),
																												tes.d.harbord = cor(pval.d.tes, pval.harbord),
																												schwarzer.peter = cor(pval.schwarzer, pval.peter),
																												schwarzer.rucker = cor(pval.schwarzer, pval.rucker),
																												schwarzer.harbord = cor(pval.schwarzer, pval.harbord),
																												rucker.peter = cor(pval.rucker, pval.peter),
																												harbord.peter = cor(pval.harbord, pval.peter))
rsquared.bin <- meta.bin %>%ungroup() %>%  summarise(tes.d.schwarzer = summary(lm(pval.d.tes~ pval.schwarzer))$r.squared,
                                                        tes.d.peter = summary(lm(pval.d.tes~ pval.peter))$r.squared,
                                                        tes.d.rucker = summary(lm(pval.d.tes~ pval.rucker))$r.squared,
                                                        tes.d.harbord = summary(lm(pval.d.tes~ pval.harbord))$r.squared,
                                                        schwarzer.peter = summary(lm(pval.schwarzer~ pval.peter))$r.squared,
                                                        schwarzer.rucker = summary(lm(pval.schwarzer~ pval.rucker))$r.squared,
                                                        schwarzer.harbord = summary(lm(pval.schwarzer~ pval.harbord))$r.squared,
                                                        rucker.peter = summary(lm(pval.rucker~ pval.peter))$r.squared,
                                                        harbord.peter = summary(lm(pval.harbord~ pval.peter))$r.squared)

binary.tests.agreement <- rbind(agreement.bin, correlation.bin, rsquared.bin)
rownames(binary.tests.agreement) <- c("Test Agreement","p-value Correlation", "p-value R-squared")
colnames(binary.tests.agreement) <- c("Excess significance, Schwarzer", "Excess significance, Peter",
                                      "Excess significance, Rucker", "Excess significance, Harbord",
                                      "Peter, Schwarzer", "Schwarzer, Rucker", "Schwarzer, Harbord",
                                      "Rucker, Peter", "Harbord, Peter")
#--------------------------------------------------------------------------------------------------------------------#

#Continuous:
meta.cont <- meta.cont %>% ungroup() %>% mutate(thompson.egger = ifelse(thompson.test == egger.test, "agree", "disagree"),
																								thompson.begg = ifelse(thompson.test == begg.test, "agree", "disagree"),
																								egger.begg = ifelse(egger.test == begg.test, "agree", "disagree"),
																								tes.d.egger = ifelse(tes.d.test == egger.test, "agree", "disagree"),
																								thompson.tes.d = ifelse(thompson.test ==tes.d.test, "agree", "disagree"),
																								tes.d.begg = ifelse(tes.d.test == begg.test, "agree", "disagree"))
agreement.cont <- meta.cont %>% ungroup() %>%  summarise(tes.d.egger = sum(tes.d.egger == "agree")/n(),
																												 thompson.tes.d = sum(thompson.tes.d == "agree")/n(),
																												 tes.d.begg = sum(tes.d.begg == "agree")/n(),
																												 thompson.egger = sum(thompson.egger == "agree")/n(),
																												 thompson.begg = sum(thompson.begg == "agree")/n(),
																												 egger.begg = sum(egger.begg == "agree")/n())
correlation.cont <- meta.cont %>% ungroup() %>% summarise(tes.d.egger = cor(pval.egger, pval.d.tes),
																													thompson.tes.d = cor(pval.thompson, pval.d.tes),
																													tes.d.begg = cor(pval.d.tes, pval.begg),
																													thompson.egger = cor(pval.thompson, pval.egger),
																													thompson.begg = cor(pval.thompson, pval.begg),
																													egger.begg = cor(pval.egger, pval.begg))
rsquared.cont <- meta.cont %>% ungroup() %>% summarise(tes.d.egger = summary(lm(pval.egger~ pval.d.tes))$r.squared,
                                                          thompson.tes.d = summary(lm(pval.thompson~ pval.d.tes))$r.squared,
                                                          tes.d.begg = summary(lm(pval.d.tes~ pval.begg))$r.squared,
                                                          thompson.egger = summary(lm(pval.thompson~ pval.egger))$r.squared,
                                                          thompson.begg = summary(lm(pval.thompson~ pval.begg))$r.squared,
                                                          egger.begg = summary(lm(pval.egger~ pval.begg))$r.squared)

cont.tests.agreement <- rbind(agreement.cont, correlation.cont, rsquared.cont)
rownames(cont.tests.agreement) <- c("Test Agreement","p-value Correlation", "p-value R-squared")
colnames(cont.tests.agreement) <- c( "Excess significance, Egger", "Excess significance, Thompson", 
                                     "Excess significance, Begg","Thompson, Egger", "Thompson, Begg", "Egger, Begg")

#Survival:
meta.surv <- meta.surv %>% ungroup() %>% mutate(thompson.egger = ifelse(thompson.test == egger.test, "agree", "disagree"),
                                                thompson.begg = ifelse(thompson.test == begg.test, "agree", "disagree"),
                                                egger.begg = ifelse(egger.test == begg.test, "agree", "disagree"),
                                                tes.d.egger = ifelse(tes.d.test == egger.test, "agree", "disagree"),
                                                thompson.tes.d = ifelse(thompson.test ==tes.d.test, "agree", "disagree"),
                                                tes.d.begg = ifelse(tes.d.test == begg.test, "agree", "disagree"))
agreement.surv <- meta.surv %>% ungroup() %>%  summarise(tes.d.egger = sum(tes.d.egger == "agree")/n(),
                                                         thompson.tes.d = sum(thompson.tes.d == "agree")/n(),
                                                         tes.d.begg = sum(tes.d.begg == "agree")/n(),
                                                         thompson.egger = sum(thompson.egger == "agree")/n(),
                                                         thompson.begg = sum(thompson.begg == "agree")/n(),
                                                         egger.begg = sum(egger.begg == "agree")/n())
correlation.surv <- meta.surv %>% ungroup() %>% summarise(tes.d.egger = cor(pval.egger, pval.d.tes),
																													thompson.tes.d = cor(pval.thompson, pval.d.tes),
																													tes.d.begg = cor(pval.d.tes, pval.begg),
																													thompson.egger = cor(pval.thompson, pval.egger),
																													thompson.begg = cor(pval.thompson, pval.begg),
																													egger.begg = cor(pval.egger, pval.begg))
rsquared.surv <- meta.surv %>% ungroup() %>% summarise(tes.d.egger = summary(lm(pval.egger~ pval.d.tes))$r.squared,
                                                          thompson.tes.d = summary(lm(pval.thompson~ pval.d.tes))$r.squared,
                                                          tes.d.begg = summary(lm(pval.d.tes~ pval.begg))$r.squared,
                                                          thompson.egger = summary(lm(pval.thompson~ pval.egger))$r.squared,
                                                          thompson.begg = summary(lm(pval.thompson~ pval.begg))$r.squared,
                                                          egger.begg = summary(lm(pval.egger~ pval.begg))$r.squared)

surv.tests.agreement <- rbind(agreement.surv, correlation.surv, rsquared.surv)
rownames(surv.tests.agreement) <- c("Test Agreement","p-value Correlation", "p-value R-squared")
colnames(surv.tests.agreement) <- c("Excess significance, Egger (survival)", "Excess significance, Thompson (survival)", 
                                    "Excess significance, Begg (survival)", "Thompson, Egger (survival)", 
                                    "Thompson, Begg (survival)", "Egger, Begg (survival)")

#Merging:
test.agreement <- rbind(t(binary.tests.agreement), t(cont.tests.agreement), t(surv.tests.agreement))

@@

\begin{figure}[ht!]
<<echo=FALSE, fig.height = 9>>=
grid.arrange(p.dist.bin,
             p.dist.cont,
             p.dist.surv, ncol = 1)
@
\caption{Histogram of the $p$-values for small study effect in meta-analyses. The testing method is indicated in the header, binwidth is equal to 0.1. The significant proportion based on the threshold of 0.1 is displayed inside the figures.}
\label{fig:test}
\end{figure}

The agreement/coinicidence between between small study effect and excess significance tests is often not pronounced, thus, it will be compared by different methods. This is displayed in Table \ref{test.agreement}. The row names indicate which two tests are compared. First, the column ``Test Agreement'' quantifies the overall proportion by which the two tests agree in their rejection or ``acceptance'' of the null-hypothesis. ``Test Agreement'' being equal one thus indicates equivalent results, zero no correspondence whatsoever. The second column, ``Correlation'' gives the correlation between the $p$-values. A positive correlation indicates psotive coincidence of $p$-values, negative correlation coincidence in opposite directions. However, the scale might be different for this agreement measure. The ``R-squared'' value indicates to what extent one $p$-value can be predicted by another, and ignores additive differences between $p$-values (as for correlation), as well as multiplicative constants between them (i.e. $y ~ a + b*x$, $y$ and $x$ being two $p$-values of test-statistics). An R-squared value of 1 indicates perfect fit. Importantly, the order of the variables does not matter for the $p$-values for all indicators (i.e. $p$-values for $x$ and $y$ can be exchanged and the table stays the same). If a test is completely replaceable by another, all values in a row are equal to one.

<<echo=FALSE, results='asis'>>=
print(xtable(test.agreement, align = "lccc", caption = "Agreement in significance proportion, correlation and R-squared of linear regression
             between the p-values of the publication bias tests. Horizontal lines separate binary, continuous and survival outcomes (order as in table).",
             label = "test.agreement"), hline = c(0,0,9, 15, 21), size = "footnotesize")
@

@@

@@

>>>>

<<'preamble03',include=FALSE, echo=FALSE>>=
library(knitr)
opts_chunk$set(fig.path='figure/ch03_fig',
               echo=TRUE, message=FALSE,
               fig.width=8.1, fig.height=3,
               self.contained = FALSE,
               out.width='\\textwidth-3cm',
               message=FALSE, fig.align='center',
               background="gray98", tidy=FALSE, #tidy.opts=list(width.cutoff=60),
               cache=TRUE
)
options(width=74)
@

@@

require(corrgram)

@@

cor.data <- meta.f %>% select(stat.rucker, stat.harbord, stat.peter, stat.schwarzer, stat.d.tes, 
                             stat.egger, stat.thompson, stat.begg)
colnames(cor.data) <- c("Rucker", "Harbord", "Peter", "Schwarzer", "Excess s.",  "Egger", "Thompson",
                        "Begg")

panel.pts.new <- function (x, y, corr = NULL, col.regions, cor.method, ...) 
{

  plot.xy(xy.coords(x, y), type = "p", ...)
  box(col = "lightgray")
  rect(xleft = -1.96, ybottom = -1.96, xright = 1.96, ytop = 1.96, density = NULL, angle = 45,
       col = NA, border = "white", lty = 1, lwd = 1.4, 
       ...)
  if (!is.null(corr)) 
    return()

}

# Tukey Mean difference plots;
#--------------------------------------------------------------------------------------------------------------------#

egger.thompson.plot <- meta.f %>% 
  mutate(mean = ((logit(pval.egger)+ logit(pval.thompson)))/2, 
         difference = logit(pval.egger) - logit(pval.thompson)) %>% 
  ggplot(aes(x = mean, y = difference)) + geom_point() + 
  geom_abline(aes(slope = 0, intercept = mean(difference, na.rm = T), col = "blue")) +
  geom_abline(aes(slope = 0,
                  intercept = mean(difference, na.rm = T) + 1.96*sqrt(var(difference, na.rm = T)), 
                  col = "red")) +
  geom_abline(aes(slope = 0,
                  intercept = mean(difference, na.rm = T) - 1.96*sqrt(var(difference, na.rm = T)), 
                  col = "red")) +
  # geom_smooth(method = "loess", se = F) + 
  theme_bw() + theme(legend.position = "none") +
  scale_color_manual(labels = c("systematic error", "95 % confidence intervals"), 
                     values = c("red", "blue")) +
  ggtitle(expression(paste("logit(", italic(p),"-value Egger) - logit(", italic(p), "-value Thompson)" )))
#--------------------------------------------------------------------------------------------------------------------#

harbord.rucker.plot <- meta.f %>% 
  mutate(mean = ((logit(pval.harbord)+ logit(pval.rucker)))/2, 
         difference = logit(pval.harbord) - logit(pval.rucker)) %>% 
  ggplot(aes(x = mean, y = difference)) + geom_point(size = .5) + 
  geom_abline(aes(slope = 0, intercept = mean(difference, na.rm = T), col = "blue")) +
  geom_abline(aes(slope = 0,
                  intercept = mean(difference, na.rm = T) + 1.96*sqrt(var(difference, na.rm = T)), 
                  col = "red")) +
  geom_abline(aes(slope = 0,
                  intercept = mean(difference, na.rm = T) - 1.96*sqrt(var(difference, na.rm = T)), 
                  col = "red")) +
  # geom_smooth(method = "loess", se = F) + 
  theme_bw() + theme(legend.position = "none") +
  scale_color_manual(labels = c("systematic error", "95 % confidence intervals"), 
                     values = c("red", "blue")) +
  ggtitle(expression(paste("logit(", italic(p),"-value Harbord) - logit(", italic(p), "-value Rucker)" )))
#--------------------------------------------------------------------------------------------------------------------#

harbord.excess.plot <- meta.f %>% 
  mutate(mean = ((logit(pval.harbord)+ logit(pval.d.tes)))/2, 
         difference = logit(pval.harbord) - logit(pval.d.tes)) %>% 
  ggplot(aes(x = mean, y = difference)) + geom_point(size = .5) + 
  geom_abline(aes(slope = 0, intercept = mean(difference, na.rm = T), col = "blue")) +
  geom_abline(aes(slope = 0,
                  intercept = mean(difference, na.rm = T) + 1.96*sqrt(var(difference, na.rm = T)), 
                  col = "red")) +
  geom_abline(aes(slope = 0,
                  intercept = mean(difference, na.rm = T) - 1.96*sqrt(var(difference, na.rm = T)), 
                  col = "red")) +
  # geom_smooth(method = "loess", se = F) + 
  theme_bw() + theme(legend.position = "bottom") +
  scale_color_manual(labels = c("systematic error", "95 % confidence intervals"), 
                     values = c("red", "blue")) +
  ggtitle(expression(paste("logit(", italic(p),"-value Harbord) - logit(", italic(p), "-value excess significance)" )))
#--------------------------------------------------------------------------------------------------------------------#

#Table with proportions of significant test results:
meta.f <- meta.f %>% 
mutate(test.sum.bin = tes.d.test + schwarzer.test + harbord.test + peter.test + rucker.test,
       test.sum.else = tes.d.test + egger.test + thompson.test + begg.test, 
       test.sum.bin2 = tes.d.test + harbord.test,
       test.sum.else2 = tes.d.test + egger.test, 
       test.min.bin = ifelse(schwarzer.test + harbord.test + peter.test + rucker.test > 0, 1, 0),
       test.min.else = ifelse(egger.test + thompson.test + begg.test > 0, 1, 0),
       test.min.bin2 = ifelse(test.sum.bin2 > 0, 1, 0),
       test.min.else2 = ifelse(test.sum.else2 > 0, 1, 0))

mean.min.bin <- round(mean(meta.f$test.min.bin, na.rm = T)*100, 1)
mean.min.else <- round(mean(meta.f$test.min.else, na.rm = T)*100, 1)

mean.min.bin2 <- round(mean(meta.f$test.min.bin2, na.rm = T)*100, 1)
mean.min.else2 <- round(mean(meta.f$test.min.else2, na.rm = T)*100, 1)

both.bin <- round(length(which(meta.f$test.sum.bin2 == 2))/
                    length(which(!is.na(meta.f$test.sum.bin2)))*100, 1)

both.else <- round(length(which(meta.f$test.sum.else2 == 2))/
                     length(which(!is.na(meta.f$test.sum.else2)))*100, 1)

summary.bin <- round(meta.f %>% 
  group_by(test.sum.bin) %>% summarise(n = n()) %>% select(n)/dim(meta.bin)[1] * 100, 1)

summary.else <- round(meta.f %>% group_by(test.sum.else) %>% 
                        summarise(n = n()) %>% 
                        select(n)/(dim(meta.cont)[1] + dim(meta.surv)[1]) * 100, 1)

number.sig.tests <- data.frame(number = seq(from = 0, to = 5),
                               binary = paste(summary.bin$n[-7], "%"),
                               cont = paste(c(summary.else$n[-6], NA), "%"))
colnames(number.sig.tests) <- c("Count", "Binary Outcomes", "Continuous and Survival")

meta.f <- meta.f %>% mutate(tes.d.test.b = ifelse(pval.d.tes < 0.05, 1, 0),
                            harbord.test.b = ifelse(pval.harbord < 0.05, 1, 0),
                            egger.test.b = ifelse(pval.egger < 0.05, 1, 0),
                            test.sum.bin2 = tes.d.test.b + harbord.test.b,
                            test.sum.else2 = tes.d.test.b + egger.test.b, 
                            test.min.bin2 = ifelse(test.sum.bin2 > 0, 1, 0),
                            test.min.else2 = ifelse(test.sum.else2 > 0, 1, 0))

mean.min.bin2.b <- round(mean(meta.f$test.min.bin2, na.rm = T)*100, 1)
mean.min.else2.b <- round(mean(meta.f$test.min.else2, na.rm = T)*100, 1)

both.bin.b <- round(length(which(meta.f$test.sum.bin2 == 2))/
                    length(which(!is.na(meta.f$test.sum.bin2)))*100, 1)

both.else.b <- round(length(which(meta.f$test.sum.else2 == 2))/
                     length(which(!is.na(meta.f$test.sum.else2)))*100, 1)

meta.f <- meta.f %>% mutate(egger.test = ifelse(pval.egger < 0.1/3, 1, 0),
                            thompson.test = ifelse(pval.thompson < 0.1/3, 1, 0),
                            begg.test = ifelse(pval.begg < 0.1/3, 1, 0),

                            schwarzer.test = ifelse(pval.schwarzer < 0.1/4, 1, 0),
                            rucker.test = ifelse(pval.rucker < 0.1/4, 1, 0),
                            harbord.test = ifelse(pval.harbord < 0.1/4, 1, 0),
                            peter.test = ifelse(pval.peter < 0.1/4, 1, 0),
                            test.sum.bin = tes.d.test + schwarzer.test + harbord.test + peter.test + rucker.test,
                            test.sum.else = tes.d.test + egger.test + thompson.test + begg.test, 
                            test.min.bin = ifelse(schwarzer.test + harbord.test + peter.test + rucker.test > 0, 1, 0),
                            test.min.else = ifelse(egger.test + thompson.test + begg.test > 0, 1, 0))

mean.min.bin.b <- round(mean(meta.f$test.min.bin, na.rm = T)*100, 1)
mean.min.else.b <- round(mean(meta.f$test.min.else, na.rm = T)*100, 1)

#--------------------------------------------------------------------------------------------------------------------#
#--------------------------------------------------------------------------------------------------------------------#
#--------------------------------------------------------------------------------------------------------------------#
#--------------------------------------------------------------------------------------------------------------------#
#--------------------------------------------------------------------------------------------------------------------#
#--------------------------------------------------------------------------------------------------------------------#
#--------------------------------------------------------------------------------------------------------------------#
#--------------------------------------------------------------------------------------------------------------------#

@@

\begin{figure}
<<echo=FALSE, fig.height = 9>>=
grid.arrange(p.dist.bin,
             p.dist.cont,
             p.dist.surv, ncol = 1)
@
\caption{Histogram of the $p$-values for small study effect in meta-analyses. The testing method is indicated in the header, binwidth is equal to 0.1. The significant proportion based on the threshold of 0.1 is displayed inside the figures.}
\label{fig:test}
\end{figure}

%Agreement table -> Chunck 1

It cannot be seen in Figure \ref{fig:test} if the tests used are finding small study effects/excess significance for the same meta-analyses. Especially between small study effects and excess significance tests, we expect some disagreement between tests. A simple method to check the coincidence of test results is to compare scatterplots and empirical spearman correlations between test statistics. This is done in Figure \ref{fig:test.agreement}. \\
Here, there is no separation between survival and continuous outcomes. The upper left rectangle is displaying binary outcomes and the lower right about continuous and survival outcomes.

\begin{figure}
<<echo=FALSE, fig.height = 6, warning=FALSE>>=
corrgram(cor.data, 
         upper.panel=panel.pts.new, lower.panel=panel.cor, 
         cex.labels = 1, cex = .3, cex.cor = 2, pch = 1,
         text.panel=panel.txt, cor.method = "spearman")
@
\caption{Pairs-plot for test statistics of small study effect and excess significance. The lower panel gives the spearman correlations for the different test statistics, and the upper panel displays a scatterplot. The colours indicate magnitude and direction of the correlation coefficients. The rectangle with white borders displays the area within which both tests have absolute value < 1.96.}
\label{fig:test.agreement}
\end{figure}

The observed patterns on the scatterplots differ: Excess significance and small study effect test statistics do usually not align with each other, forming rather randomly scattered bulks of points. Regression based tests as Egger and Thompson which are methodically almost identical are closely aligned, which is also reflected in large correlation coefficients. In general, small study effect tests align, but the extent to which they align differs. Harbord's test statistic has similar correlation coefficients with all other small study effect test statistics for binary outcomes, while the correlation coefficients between them is varying.\\
Because scatterplots and correlation coefficients can be missleading, also a Tukey mean-difference or Bland-Altmann plot is shown for three scenarios in Figure \ref{fig:mean.diff.test}:
\begin{itemize}
\item For Egger's and Thompson's tests, which is supposedly the most similar test and should show the least deviations and systematic errors
\item For Harbord's and Rucker's tests
\item For Harbord's and excess significance tests
\end{itemize}

This can be justified since all tests are supposed to measure the evidence for publication bias. For the plots, the $p$-values of the tests are transformed on the entire continuous scale by a logit transformation. The mean $p$-value ((logit($p$-value 1) + logit($p$-value 2))/2) is then displayed against the differnec between the $p$-value. If no systematic errors and biases exist between the measurement methods, then

\begin{itemize}
\item the mean of the differences (systematic error) should be around zero
\item the points should scatter independent of the mean of the $p$-values
\end{itemize}

The last criterium seems not to be given when comparing Harbords and Excess significance tests. 
-- In the appendix, it can be seen that this is reproducible with the remainig small study effect tests (not there yet) -- 
With decreasing mean, the difference gets more negative, and vice versa, such that one would predict that the excess significance $p$-values are more ``extreme'' in both directions. This finding suggests that correspondence between the tests is poor. The confidence intervals can be used as limits of agreement, which gives, after back-transformation, around 0.9 for Egger and Thompson test, and around 0.99 for Harbord and Rucker.

\begin{figure}
<<echo=FALSE, fig.height = 6.5, warning=FALSE>>=
grid.arrange(egger.thompson.plot, 
             harbord.rucker.plot, 
             harbord.excess.plot, ncol = 1)
@
\caption{Mean - difference plots for logit transformed $p$-values. The mean of logit transformed $p$-values is displayed on the $x$-axis and the difference on the $y$-axis. Blue and red lines display the systematic error and the confidence intervals of the systematic error (limits of agreement).}
\label{fig:mean.diff.test}
\end{figure}

The previous results suggest that the results will also differ substantially after applying the common dichotomization of $p$-values. We expect that some proportion of the meta-analysis will only be significant for a certain test, and this is indeed observed in Table \ref{number.sig.tests}. It displays the percentage of meta-analyses with a certain number of significant test results.

<<echo = FALSE, results='asis'>>=
print(xtable(number.sig.tests, caption = "Counts Number of significant test results per meta-analysis, separated
       for outcome types. Last entry for continuous and survival outcomes is empty since one test less was 
       applied", label = "number.sig.tests", align = "lccc"), include.rownames = F, size = "footnotesize")
@

When only looking at small study effect tests, \Sexpr{mean.min.bin}\% of binary outcome tests and \Sexpr{mean.min.else}\% of survival and continuous outcome tests had at least one significant result. After applying the bonferroni correction for multiple testing, this shrinks to \Sexpr{mean.min.bin.b}\& for binary and \Sexpr{mean.min.else.b}\% for continuous and survival outcomes. \\
When comparing significant findings for small study effect tests and excess significance tests, we will only do so with Harbord's or Egger's test. \Sexpr{mean.min.bin2}\% of binary outcome analyses had at least one of the two test $p$-values being significant, and equivalently, \Sexpr{mean.min.else2}\% for continuous and survival outcomes. Again, the numbers change to \Sexpr{mean.min.bin2.b}\% for binary outcomes and \Sexpr{mean.min.else2.b}\% for continuous and survival outcomes after applying the bonferroni correction. \\
\Sexpr{both.bin}\% have significant Harbord's test result and significant excesss significance test result  (\Sexpr{both.bin.b}\% with bonferroni). Of the continuous outcomes, we have \Sexpr{both.else} \% with Egger's test and \Sexpr{both.else.b} with Bonferroni correction.

@@

% %Chunck 6

@@

% meta.bin <- meta.bin %>%ungroup() %>%  mutate(tes.d.schwarzer = ifelse(tes.d.test == schwarzer.test, "agree", "disagree"),
%                                               tes.d.peter = ifelse(tes.d.test == peter.test, "agree", "disagree"),
%                                               tes.d.rucker = ifelse(tes.d.test == rucker.test, "agree", "disagree"),
%                                               tes.d.harbord = ifelse(tes.d.test == harbord.test, "agree", "disagree"),
% agreement.bin <- meta.bin %>% ungroup() %>% summarise(tes.d.schwarzer = sum(tes.d.schwarzer == "agree")/n(),
%                                                       tes.d.peter = sum(tes.d.peter == "agree")/n(),
%                                                       tes.d.rucker = sum(tes.d.rucker == "agree")/n(),
%                                                       tes.d.harbord = sum(tes.d.harbord == "agree")/n(),
% correlation.bin <- meta.bin %>%ungroup() %>%  summarise(tes.d.schwarzer = cor(stat.d.tes, stat.schwarzer),
%                                                         tes.d.peter = cor(stat.d.tes, stat.peter),
%                                                         tes.d.rucker = cor(stat.d.tes, stat.rucker),
%                                                         tes.d.harbord = cor(stat.d.tes, stat.harbord),
%                                                         schwarzer.peter = cor(stat.schwarzer, stat.peter),
%                                                         schwarzer.rucker = cor(stat.schwarzer, stat.rucker),
%                                                         schwarzer.harbord = cor(stat.schwarzer, stat.harbord),
%                                                         rucker.peter = cor(stat.rucker, stat.peter),
%                                                         harbord.peter = cor(stat.harbord, stat.peter))
% # rsquared.bin <- meta.bin %>%ungroup() %>%  summarise(tes.d.schwarzer = summary(lm(stat.d.tes~ stat.schwarzer))$r.squared,
% #                                                         tes.d.peter = summary(lm(stat.d.tes~ stat.peter))$r.squared,
% #                                                         tes.d.rucker = summary(lm(stat.d.tes~ stat.rucker))$r.squared,
% #                                                         tes.d.harbord = summary(lm(stat.d.tes~ stat.harbord))$r.squared,
% #                                                         schwarzer.peter = summary(lm(stat.schwarzer~ stat.peter))$r.squared,
% #                                                         schwarzer.rucker = summary(lm(stat.schwarzer~ stat.rucker))$r.squared,
% #                                                         schwarzer.harbord = summary(lm(stat.schwarzer~ stat.harbord))$r.squared,
% #                                                         rucker.peter = summary(lm(stat.rucker~ stat.peter))$r.squared,
% #                                                         harbord.peter = summary(lm(stat.harbord~ stat.peter))$r.squared)
% meta.bin <- meta.bin %>%ungroup() %>%  mutate(tes.d.schwarzer = ifelse(tes.d.test + schwarzer.test > 1, "agree", "disagree"),
%                                               tes.d.peter = ifelse(tes.d.test + peter.test > 1, "agree", "disagree"),
%                                               tes.d.rucker = ifelse(tes.d.test + rucker.test > 1, "agree", "disagree"),
%                                               tes.d.harbord = ifelse(tes.d.test + harbord.test > 1, "agree", "disagree"),
%                                               schwarzer.peter = ifelse(schwarzer.test + peter.test > 1, "agree", "disagree"),
%                                               schwarzer.rucker = ifelse(schwarzer.test + rucker.test > 1, "agree", "disagree"),
%                                               schwarzer.harbord = ifelse(schwarzer.test + harbord.test > 1, "agree", "disagree"),
%                                               rucker.peter = ifelse(rucker.test + peter.test > 1, "agree", "disagree"),
%                                               rucker.harbord = ifelse(rucker.test + harbord.test > 1, "agree", "disagree"),
%                                               harbord.peter = ifelse(harbord.test + peter.test > 1, "agree", "disagree"))
% agreement.bin <- meta.bin %>% ungroup() %>% summarise(tes.d.schwarzer = sum(tes.d.schwarzer == "agree")/sum(schwarzer.test),
%                                                       tes.d.peter = sum(tes.d.peter == "agree")/sum(peter.test),
%                                                       tes.d.rucker = sum(tes.d.rucker == "agree")/n(),
%                                                       tes.d.harbord = sum(tes.d.harbord == "agree")/n(),
% binary.tests.agreement <- rbind(agreement.bin, correlation.bin, rsquared.bin)
% rownames(binary.tests.agreement) <- c("Test Agreement","p-value Correlation", "p-value R-squared")
% colnames(binary.tests.agreement) <- c("Excess significance, Schwarzer", "Excess significance, Peter",
%                                       "Excess significance, Rucker", "Excess significance, Harbord",
%                                       "Peter, Schwarzer", "Schwarzer, Rucker", "Schwarzer, Harbord",
%                                       "Rucker, Peter", "Harbord, Peter")
% #--------------------------------------------------------------------------------------------------------------------#
% meta.cont <- meta.cont %>% ungroup() %>% mutate(thompson.egger = ifelse(thompson.test == egger.test, "agree", "disagree"),
%                                                 thompson.begg = ifelse(thompson.test == begg.test, "agree", "disagree"),
%                                                 egger.begg = ifelse(egger.test == begg.test, "agree", "disagree"),
%                                                 tes.d.egger = ifelse(tes.d.test == egger.test, "agree", "disagree"),
%                                                 thompson.tes.d = ifelse(thompson.test ==tes.d.test, "agree", "disagree"),
%                                                 tes.d.begg = ifelse(tes.d.test == begg.test, "agree", "disagree"))
% agreement.cont <- meta.cont %>% ungroup() %>%  summarise(tes.d.egger = sum(tes.d.egger == "agree")/n(),
%                                                          thompson.tes.d = sum(thompson.tes.d == "agree")/n(),
%                                                          tes.d.begg = sum(tes.d.begg == "agree")/n(),
%                                                          thompson.egger = sum(thompson.egger == "agree")/n(),
%                                                          thompson.begg = sum(thompson.begg == "agree")/n(),
% correlation.cont <- meta.cont %>% ungroup() %>% summarise(tes.d.egger = cor(stat.egger, stat.d.tes),
%                                                           thompson.tes.d = cor(stat.thompson, stat.d.tes),
%                                                           tes.d.begg = cor(stat.d.tes, stat.begg),
%                                                           thompson.egger = cor(stat.thompson, stat.egger),
%                                                           thompson.begg = cor(stat.thompson, stat.begg),
%                                                           egger.begg = cor(stat.egger, stat.begg))
% rsquared.cont <- meta.cont %>% ungroup() %>% summarise(tes.d.egger = summary(lm(stat.egger~ stat.d.tes))$r.squared,
%                                                        thompson.tes.d = summary(lm(stat.thompson~ stat.d.tes))$r.squared,
%                                                        tes.d.begg = summary(lm(stat.d.tes~ stat.begg))$r.squared,
%                                                        thompson.egger = summary(lm(stat.thompson~ stat.egger))$r.squared,
%                                                        thompson.begg = summary(lm(stat.thompson~ stat.begg))$r.squared,
%                                                        egger.begg = summary(lm(stat.egger~ stat.begg))$r.squared)
% agreement.sig.cont <- meta.cont %>% ungroup() %>%  summarise(tes.d.egger = sum(tes.d.egger == "agree")/sum(egger.test),
%                                                              thompson.tes.d = sum(thompson.tes.d == "agree")/sum(thompsom.test),
%                                                              tes.d.begg = sum(tes.d.begg == "agree")/sum(begg.test),
%                                                              thompson.egger = sum(thompson.egger == "agree")/sum(egger.test),
%                                                              thompson.begg = sum(thompson.begg == "agree")/sum(thompson.test),
%                                                              egger.begg = sum(egger.begg == "agree")/sum(egger.test))
% cont.tests.agreement <- rbind(agreement.cont, correlation.cont, rsquared.cont)
% rownames(cont.tests.agreement) <- c("Test Agreement","p-value Correlation", "p-value R-squared")
% colnames(cont.tests.agreement) <- c( "Excess significance, Egger", "Excess significance, Thompson", 
%                                      "Excess significance, Begg","Thompson, Egger", "Thompson, Begg", "Egger, Begg")
% #--------------------------------------------------------------------------------------------------------------------#
% #Survival:
% meta.surv <- meta.surv %>% ungroup() %>% mutate(thompson.egger = ifelse(thompson.test == egger.test, "agree", "disagree"),
%                                                 thompson.begg = ifelse(thompson.test == begg.test, "agree", "disagree"),
%                                                 egger.begg = ifelse(egger.test == begg.test, "agree", "disagree"),
%                                                 tes.d.egger = ifelse(tes.d.test == egger.test, "agree", "disagree"),
%                                                 thompson.tes.d = ifelse(thompson.test ==tes.d.test, "agree", "disagree"),
%                                                 tes.d.begg = ifelse(tes.d.test == begg.test, "agree", "disagree"))
% agreement.surv <- meta.surv %>% ungroup() %>%  summarise(tes.d.egger = sum(tes.d.egger == "agree")/n(),
%                                                          thompson.tes.d = sum(thompson.tes.d == "agree")/n(),
%                                                          tes.d.begg = sum(tes.d.begg == "agree")/n(),
